\documentclass[14pt]{article}
%\usepackage[margin = 0.8in]{geometry}
\usepackage[a4paper, left=1in, right=0.7in, top=0.8in, bottom=0.8in]{geometry}
%\usepackage{fontspec} must use Xelatex compiler
%\usepackage[osf]{mathpazo}
%\usepackage{fancyheadings}
\usepackage[normalem]{ulem}
\usepackage{enumerate}
\usepackage{verbatim}
%\setmainfont[Numbers=OldStyle]{TeX Gyre Pagella} must use Xelatex compiler
\usepackage{tabularx}
%\usepackage[document]{ragged2e}
%\pagestyle{fancy}
\pagenumbering{arabic}
\oddsidemargin 0.0in 
\evensidemargin 0.0in 
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}


\begin{document}
%\renewcommand{\headrulewidth}{0pt}
%\renewcommand{\footrulewidth}{0.5pt}
%\lfoot{}
%\cfoot{}
%\rfoot{\thepage}
\title{Curriculum Vitae}

\begin{tabularx}{\textwidth}{l r}
\Huge{\textbf{Sumukha Tumkur Vani}} & 
\large
\begin{tabular}{r}
371, 10$^{th}$ cross\\
Mahalakshmi Layout\\
Bangalore 560086\\
India\\
Phone: +91 80 2349 8309\\
Mobile: +91 95 91 636530\\
E-mail: sumukhatv@live.com
\end{tabular}
\end{tabularx}
\rule{\textwidth}{0pt}
\rule{\textwidth}{0.4pt}

\subsection* {\scshape\LARGE\uline {Education}}
\large

\begin{tabular}{r l}
\emph{2010 - 2014} & \textbf{Bachelor of Engineering} \\
		                  & Major: Computer Science and Engineering\\ 
			            & Bangalore University, India \\
			            & Graduated with 83.8\% [GPA: 3.67/4.0]			    
\\ \\

\emph{2008 - 2010} & \textbf{Pre-University Course} \\ 
		                  & MES Pre-University College, Bangalore, India \\
			            & 2$^{nd}$PUC 93\%		    
\\ \\

\emph{2005 - 2008} & \textbf{High School} \\ 
			            & VVS Sardar Patel High School, Bangalore, India \\
				      & SSLC 95.36\%		    
\end{tabular}


\subsection* {\scshape\LARGE\uline {Professional Experience}}
\large
\begin{tabularx}{\textwidth}{r X}
\emph{2014 - Present} & \textbf{Software Developer}, \textit{Oracle India Pvt Ltd}, Bangalore, India \\
		                      & Oracle Virtual Networking\\ 
			                & $\bullet$ Involved in the development of Infiniband products\\
			                & $\bullet$ Involved in building device drivers and system softwares for  Solaris OS\\
			                & $\bullet$ Experience of coding on the SPARC machines	    
\\ \\

\emph{2013 - 2014} & \textbf{Software Developer Intern}, \textit{Streamoid Technologies}, Bangalore, India \\ 
			            & $\bullet$ Worked on Natural Language Processing tools \\
		 	            & $\bullet$ Designed and developed a search engine using Apache Solr \\
   			            & $\bullet$ Implemented and analysed product recommendation systems \\
			            & $\bullet$ Built a performance and load testing system using Apache JMeter
\\ \\

\emph{2012 - 2013} & \textbf{Software Developer Intern}, \textit{Teritree Technologies}, Bangalore, India \\ 
			            & $\bullet$ Developed a database web application on the Amazon EC2 \\
			            & $\bullet$ Developed an email application using the Amazon SES\\
			            & $\bullet$ Built an extension for the Google Chrome web browser	    
\end{tabularx}

\subsection* {\scshape\LARGE\uline {Technical Skills}}
\begin{tabular}{r l}
\emph{Programming} & C, C++, Java, Python \\
\emph{Web}              & HTML, PHP, Javascript \\
\emph{Database}	  & MySQL, MongoDB \\
\emph{Operating Systems} & Solaris, Linux, Windows
\end{tabular}

\subsection* {\scshape\LARGE\uline {Awards and Honors}}
\begin{tabularx}{\textwidth}{r X}
\emph{Nov 2014} & \textbf{Excellent Paper Award} and \textbf{Gold Medal} for the research paper  titled ``\emph{DSWSD: Double Sliding Window for Secure Data Transmission in WSNs}'', at the International Conference of Science, Technology, Engineering and Management, Singapore. \\ \\
\emph{June 2014} & \textbf{Best Under Graduate project} for ``\emph{Adaptive Load Balancing Protocol for Service Oriented Wireless Sensor Networks}" \\ \\
\emph{Dec 2013} & Winner of SAP Lumira University Challenge 2013. \\ \\
\emph{Jan 2013} & Held the \textbf{Collaboration Platform Lead} position in the Student Activities Committee for the year 2013-2014 in the IEEE Bangalore Section. 
\end{tabularx}

\subsection* {\scshape\LARGE\uline {Publications}}
\begin{tabularx}{\textwidth}{r X}
\emph{Feb 2015} & Lata B T, \textbf{Sumukha T V}, Suhas H, Tejaswi V, Shaila K, Venugopal K R, L M Patnaik ``\textbf{\textit{SALB: Secure Adaptive Load 		         Balancing in Service Oriented Wireless Sensor Networks}}",  IEEE Signal Processing, Informatics, Communication and Energy Systems Conference Proceedings \\ \\
\emph{Nov 2014} & Lata B T, \textbf{Sumukha T V}, Suhas H, Raghavendra M, Shaila K, Venugopal K R, L M Patnaik, ``\textbf{\textit{DSWSD: Double Sliding Window for Secure Data Transmission in WSNs}}", International Journal of Computer Networking, Wireless and Mobile Communications (IJCNWMC) \\ \\
\emph{Nov 2014} & Lata B T, Raghavendra M,  \textbf{Sumukha T V}, Suhas H, Tejaswi V, Shaila K, Venugopal K R, L M Patnaik, `` \textbf{\textit{DRFSD: Directed Restricted Flooding for Secure Data-aggregation in Wireless Sensor Networks}}", International Journal of Computer Networking, Wireless and Mobile Communications (IJCNWMC)
\end{tabularx}

\subsection* {\scshape\LARGE\uline {Projects}}
\begin{tabularx}{\textwidth}{r X}
\emph{Computer} & \textbf{Adaptive Load Balancing Protocol for Service Oriented Wireless} \\
\emph{Networks} & \textbf{Sensor Networks} \\
                             & $\bullet$  An efficient load balancing protocol for routing data in a WSN. \\
                             & $\bullet$ Introduced a technique to deduce and evaluate a set of link disjoint paths from all available paths. \\
				   & $\bullet$ Congestion detection and control by adaptive load ditribution over multipath. \\
\\
\emph{Computer} & \textbf{SSexecutor, A multi-platform project testing tool} \\
\emph{Networks} & $\bullet$ A remote machine program execution system meant to facilitate code testing on multiple machines. \\
                             & $\bullet$ Copies a project from local machine to a remote machine and executes it. \\
				   & $\bullet$ Brings back the console output from the remote machine to the local machine. \\
\\
\emph{System} & \textbf{SSASM, A Complete SIC Machine Assembler} \\
\emph{Software} & $\bullet$ Implementation of a Simple Instruction Set machine compatible assembler. \\
				& $\bullet$ Includes a technique to detect errors in the source code. \\
				& $\bullet$ Produces an object file which is ready for loading. 
\end{tabularx}
\end{document}